Minimal trap spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-06-15 cmsb22.tex
Conclusion
v_i(t+1)

%%% Boolean model %%%
Given a Boolean model \(\mathcal{M} = (V, F)\) with nodes \(V=(v_{1},\dots,v_{n})\) and Boolean functions \(F=(f_{1},\dots,f_{n})\), its state-space is \(\mathcal{S}_{\mathcal{M}} =\mathbb{B}^{n}\) with \(\mathbb{B} = \{0, 1\}\). A state \(s \in \mathbb{B}^{n}\) is a mapping \(s : V \mapsto \mathbb{B}\) that assigns either 0 (inactive) or 1 (active) to each node. At each time step \(t\), node \(v_i\) can update its state by
\[v_i(t + 1) = f_i(v(t)),\] where \(v(t)\) is the state of \(\mathcal{M}\) at time \(t\) and \(v_i(t + 1)\) the state of node \(v_i\) at time \(t + 1\). An update scheme of a Boolean model specifies the way that the nodes of the model update their states through time evolution~\cite{thomas1991regulatory}. There are two main types of update schemes: synchronous and asynchronous.

@@

>>>>

%%% Boolean model %%%
Given a Boolean model \(\mathcal{M} = (V, F)\) with nodes \(V=(v_{1},\dots,v_{n})\) and Boolean functions \(F=(f_{1},\dots,f_{n})\), its state-space is \(\mathcal{S}_{\mathcal{M}} =\mathbb{B}^{n}\) with \(\mathbb{B} = \{0, 1\}\). A state \(s \in \mathbb{B}^{n}\) is a mapping \(s \colon V \mapsto \mathbb{B}\) that assigns either 0 (inactive) or 1 (active) to each node. At each time step \(t\), node \(v_i\) can update its state by
\revise{\[v_i(t + 1) \in \{v_{i}(t), f_i(v(t))\}\]
where \(v(t)\) is the state of \(\mathcal{M}\) at time \(t\), \(v_i(t + 1)\) the state of node \(v_i\) at time \(t + 1\) and an update scheme specifies which value is chosen~\cite{thomas1991regulatory}.
There are two main types of update schemes: synchronous, where for all \(i, v_{i}(t+1) = f_{i}(v(t))\), and asynchronous, where an \(i\) is chosen among the possible updates (\(f_{i}(v(t))\neq v_{i}(t)\)), and all the other nodes \(j\) remain fixed at \(v_{j}(t)\).}

@@

\revise{Finally, we think that the links between Petri nets and Boolean models that we stumbled upon in this method might have deeper roots. Exploring those connections might lead both to interesting topics of research for Petri nets, like a notion of trap-spaces, and for Boolean models.}
